\EVOSUITE at the SBFT 2023 Tool Competition

### 2023-03-15 papers/sbst23/paper_sbst23.tex
Fix results section

Among the tests for \Collections the longest one was produced by \EVOSUITE.
Interestingly, it ranked both highest and lowest, with one participant
stating it was ``the most complete'', while another suggested the code
being longer makes it ``more confusing''.

As a general trend, participants seem to value expressive names for test cases
variables, separation of concerns (i.e., unrelated functionality is )
and meaningful assertions.

shorter tests

>>>>

Among the tests for \Collections the longest one was produced by \EVOSUITE.
Interestingly, it ranked both highest and lowest, with one participant
stating it was ``the most complete'', while another suggested the code
being longer makes it ``more confusing''. But as a general trend, participants
seemed to prefer shorter, more cohesive tests with assertions that only check
one particular aspect of the method under test.
